Search-Based Test Data Generation for JavaScript Functions that Interact with the DOM \thanks{Identify applicable funding agency here. If none, delete this.}

### 2018-08-11 doc/issre2018/introduction.tex
Preparing camera ready: introduction

According to the \emph{StackOverflow} Developer Survey 2018 \cite{stackoverflow2018}, JavaScript has been recognized for the sixth time in row as the most commonly used programming language. It is also the most popular language on \emph{GitHub}~\cite{guthub2017} based on the number of opened pull requests (2.3 million). The success of JS can be explained by its native browsers support, and the rise in popularity of the JS run-time environment \emph{Node.js}. On the other hand, due to of implicit type conversion, lack of static types, and extensive support of dynamic language constructs~\cite{richards2010analysis}, JS applications are often error-prone~\cite{frolin:TSE16}, hard to analyze~\cite{andreasen2017survey, sun2017analysis} and test~\cite{mesbah2015advances}. Thus, it is not surprising that once in a while critical bugs manage to break through~\cite{bugstories2017} even into the web applications of major companies such as Facebook, Twitter etc.

Systematic unit testing is a basic and, at the same time, the most effective technique for improving software quality~\cite{martin2009clean}. There exist numerous JS frameworks on the market --- Mocha, Jasmine, Jest, Enzyme, Tape, Ava, Karma, QUnit etc. --- intended to assist web developers with the automation of various  activities such as the design, execution and monitoring of unit tests. Despite the apparent abundance of the JS testing tools, the developers' satisfaction rate is still relative low~\cite{stateJS2017} (3.2 out of 5), suggesting the need for improvements. One of the missing steps on the way to complete JS test automation is \emph{the generation of test data}. It pursues the goal of maximizing test coverage by exercising the function under test (FUT) with various input parameters. Moreover, if a FUT interacts with the DOM of a web application, a \emph{test fixture} is expected as an additional input.

Generally, the problem of test data generation has been actively studied for the past three decades. In particular for JS, researchers have proposed several solutions based on: concolic execution (\emph{Jalangi}~\cite{sen2013jalangi}, \emph{Confix}~\cite{amin:ase15}), random generation (\emph{JSContest}~\cite{heidegger2010contract}), and the analysis of the whole web application (\emph{Artemis}~\cite{artemis2011}, Crawljax~\cite{mesbah2012crawling}). Out of those tools, only \emph{Confix} tries to construct sufficient DOM fixtures by encoding browser API calls as logical constraints. However, the empirical validation of Confix~\cite{amin:ase15} has shown that it only reached about 50\% \emph{branch coverage} on the selected subjects. At the same time, search-based techniques have shown prominent results in successfully achieving higher branch coverage for imperative~\cite{wegener2001evolutionary}, object-oriented~\cite{fraser2011evosuite} and dynamic languages~\cite{irawan2016test, wibowo2015unit}, as well as for web~\cite{alshahwan2011automated} and mobile~\cite{mao2016sapienz} applications. But to the best of our knowledge, the problem of test data generation has never been tackled for JS with the help of the search-based approach. In this paper we are breaching this gap by introducing a \textbf{J}avascript \textbf{E}volution-based testing framework with \textbf{D}OM as an \textbf{I}nput, called \emph{JEDI}. We can summarize our contributions as follows:
\begin{enumerate}[leftmargin=5mm]
\item The \emph{JEDI} framework is a novel JS unit testing tool using search-based techniques for generating test data. Notably, our testing framework is able to generate an arbitrary DOM input (both tags and attributes), which is syntactically valid and compliant with the recent HTML5 specification.
\item Our test generation algorithm, called ``genetic with restart'', attempts to escape a plateau by restarting the search with a new target. In contrast with the \emph{chaining approach}~\cite{ferguson1996chaining}, we choose the new target purely based on the preceding control flow behaviour because a full-fledged data flow analysis~\cite{jang2009points} of JS is hardly reachable.
\item Based on the case studies found in two related works~\emph{Confix}~\cite{amin:ase15} and \emph{TAJS}~\cite{dom2011}, we conducted an empirical validation of our framework and performed a significance study of the results. The validation has shown the effectiveness of the framework in covering target branches with a reasonable efficiency. Moreover, we show that out of 10 functions where \emph{JEDI} achieved complete branch coverage, \emph{Confix} only covered 32\% on average.
\end{enumerate}

>>>>

According to the \emph{StackOverflow} Developer Survey 2018 \cite{stackoverflow2018}, JavaScript has been recognized for the sixth time in row as the most commonly used programming language. It is also the most popular language on \emph{GitHub}~\cite{guthub2017} based on the number of opened pull requests (2.3 million). The success of JS can be explained by its native browsers support, and the rise in popularity of the JS run-time environment \emph{Node.js}. On the other hand, due to implicit type conversion, lack of static types, and extensive support of dynamic language constructs~\cite{richards2010analysis}, JS applications are often error-prone~\cite{frolin:TSE16}, hard to analyze~\cite{andreasen2017survey, sun2017analysis} and test~\cite{mesbah2015advances}. Thus, it is not surprising that once in a while critical bugs manage to make it into web applications of major companies such as Facebook, Twitter etc~\cite{bugstories2017}.

Systematic unit testing is a basic and, at the same time, the most effective technique for improving software quality~\cite{martin2009clean}. There exist numerous JS frameworks on the market --- Mocha, Jasmine, Jest, Enzyme, Tape, Ava, Karma, QUnit etc. --- intended to assist web developers with the automation of various  activities such as the design, execution and monitoring of unit tests. Despite the apparent abundance of the JS testing tools, developers' satisfaction rate is still relative low~\cite{stateJS2017} (3.2 out of 5), suggesting the need for improvements. One of the missing steps on the way to complete JS test automation is \emph{the generation of test data}. It pursues the goal of maximizing test coverage by exercising the function under test (FUT) with various input parameters. Moreover, if a FUT interacts with the DOM of a web application, a \emph{test fixture} is expected as an additional input.

The problem of test data generation has been actively studied for the past three decades. In particular for JS, researchers have proposed several solutions based on: concolic execution (\emph{Jalangi}~\cite{sen2013jalangi}, \emph{Confix}~\cite{amin:ase15}), random generation (\emph{JSContest}~\cite{heidegger2010contract}), and the analysis of the complete web application (\emph{Artemis}~\cite{artemis2011}, Crawljax~\cite{mesbah2012crawling}). Out of those tools, only \emph{Confix} tries to construct sufficient DOM fixtures by encoding browser API calls as logical constraints. However, the empirical validation of Confix~\cite{amin:ase15} has shown that it only reaches about 50\% \emph{branch coverage} on the selected subjects. At the same time, search-based techniques have shown prominent results in successfully achieving higher branch coverage for imperative~\cite{wegener2001evolutionary}, object-oriented~\cite{fraser2011evosuite} and dynamic languages~\cite{irawan2016test, wibowo2015unit}, as well as for web~\cite{alshahwan2011automated} and mobile~\cite{mao2016sapienz} applications. But to the best of our knowledge, the problem of test data generation has never been tackled for JS with the help of search-based approach. In this paper we are bridging this gap by introducing a \textbf{J}avascript \textbf{E}volution-based testing framework with \textbf{D}OM as an \textbf{I}nput, called \emph{JEDI}. We summarize our contributions as follows:
\begin{enumerate}[leftmargin=5mm]
\item The \emph{JEDI} framework is a novel JS unit testing tool using search-based techniques for generating test data. Notably, our testing framework is able to generate an arbitrary DOM input (both tags and attributes), which is syntactically valid and compliant with the recent HTML5 specification.
\item Our test generation algorithm, called ``genetic with restart'', attempts to escape a plateau by restarting the search with a new target. In contrast to the \emph{chaining approach}~\cite{ferguson1996chaining}, we choose the new target purely based on the preceding control flow behaviour because a full-fledged data flow analysis~\cite{jang2009points} of JS is hardly achievable.
\item Based on the case studies found in two related papers~\emph{Confix}~\cite{amin:ase15} and \emph{TAJS}~\cite{dom2011}, we conducted an empirical validation of our framework and performed a significance study of the results. The validation shows the effectiveness of the framework in covering target branches with a reasonable efficiency. Moreover, we show that out of 10 functions where \emph{JEDI} achieved complete branch coverage, \emph{Confix} only covered 32\% on average.
\end{enumerate}

### 2018-08-11 doc/issre2018/issre2018.tex
Preparing camera ready: introduction

\begin{abstract}
The popularity of JavaScript is continuously growing. Together with HTML and CSS, it is the core technology for modern web development. Because of the dynamic nature and complex interplay with HTML, JS applications are often error-prone and vulnerable. Despite the active research efforts to devise intricate static and dynamic analyses to facilitate JS testing, the problem of test data generation for JS code interacting with the DOM has not yet been addressed. In this paper, we present a novel \textbf{J}avascript \textbf{E}volution-based testing framework with \textbf{D}OM as an \textbf{I}nput, called \emph{JEDI}. In order to reach a target branch, it applies genetic search for relevant input parameters of the JS function including the global DOM state. We conducted an empirical evaluation to study the effectiveness and efficiency of our testing framework. It shows that the \emph{genetic with restart} algorithm, proposed in this paper, is able to achieve complete branch coverage for all experimental subjects, taking on average 19 seconds per branch.
\end{abstract}

>>>>

\begin{abstract}
The popularity of JavaScript is enormous. Together with HTML and CSS, it is the core technology for modern web development. Because of the dynamic nature and complex interplay with HTML, JS applications are often error-prone and vulnerable. Despite active research efforts to devise intricate static and dynamic analyses to facilitate JS testing, the problem of test data generation for JS code interacting with the DOM has not yet been addressed. In this paper, we present a \textbf{J}avascript \textbf{E}volution-based testing framework with \textbf{D}OM as an \textbf{I}nput, called \emph{JEDI}. In order to reach a target branch, it applies genetic search for relevant input parameters of the JS function in combination with the global DOM state. We conducted an empirical evaluation to study the effectiveness and efficiency of our testing framework. It shows that the \emph{genetic with restart} algorithm, proposed in this paper, is able to achieve complete branch coverage for all experimental subjects, taking on average 19 seconds per branch.
\end{abstract}
